An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-31 main.tex
formatting changes
Minor changes

\vspace{-10pt}
\input {intro}
\vspace{-10pt}
\input {tauroast}
\vspace{-10pt}
\input {observation}
\vspace{-10pt}
\input {evolution}
\vspace{-10pt}
\input {measure}
\vspace{-10pt}
\input {evaluation}
\vspace{-10pt}
\input {related_work}
\vspace{-10pt}
\section{Conclusions and Future work}
In this paper, we propose an invariant framework for conducting reproducible computational science - using light-weight virtualization approaches to preserve applications in the format of self-contained packages and using standardized software delivery mechanisms to deliver and distribute preserved packages.
We use two complex high energy physics applications to illustrate how the framework can help the original authors preserve and distribute the applications, and others reproduce the applications.
This paper focuses on how to measure the mess and track the used dependencies to preserve an application.
In the following work, we plan to explore how to preserve an application in an organized style - specifying the execution environment clearly.
How to preserve and improve the availability of remote network resources is another important problem to be explored.

\small
\vspace{-10pt}
DOI for the experiment involved in the paper: \url{doi:10.7274/R0C24TCG}

>>>>

\vspace{-10pt}
\input {intro}
\vspace{-10pt}
\input {tauroast}
\vspace{-10pt}
\input {observation}
\vspace{-10pt}
\input {evolution}
\vspace{-10pt}
\input {measure}
\vspace{-10pt}
\input {evaluation}
\vspace{-10pt}
\input {related_work}
\vspace{-10pt}
\section{Conclusions and Future work}
In this paper, we propose an invariant framework for conducting reproducible computational science - using light-weight virtualization approaches to preserve applications in the format of self-contained packages and using standardized software delivery mechanisms to deliver and distribute preserved packages.
We use two complex high energy physics applications to illustrate how the framework can help the original authors preserve and distribute the applications, and others reproduce the applications.

This paper focuses on how to measure the mess and track the used dependencies to preserve an application.
In the following work, we plan to explore how to preserve an application in an organized style - specifying the execution environment clearly.
How to preserve and improve the availability of remote network resources is another important problem to be explored.

The DOI name for the experiment involved in the paper is \url{doi:10.7274/R0C24TCG}, and current information may be found on the web through \url{http://doi.org/doi:10.7274/R0C24TCG}.

The Athena experiment is further preserved at:

\indent \indent \indent \indent \indent \url{https://sites.google.com/site/invariantcompatlas/}
